Liste des enquêtes

### 2025-03-10 report/CONJ_COMD.qmd
template update

		rev_tot <- lapply(series, function(serie) {
			rev_by_method <- lapply(names(studied_methods), function(method){
				data <- rev_data_fixed[[serie]][[method]]
				data_tot <- rev_data[[serie]][[method]]
				rev_tc <- (data[,1] - data)
				rev_tot <- (data_tot[,1] - data_tot)
				rev_tot <- rev_tot
				rev_sa <- rev_tot - rev_tc
				colnames(rev_tc) <- colnames(rev_sa) <- colnames(rev_tot) <- colnames(data_tot)
				list(
					Total = rev_tot, 
					`Due to revisions on SA` = rev_sa, 
					`Due to update of TC model` = rev_tc
				)
			})
			names(rev_by_method) <- names(studied_methods)
			rev_tot_by_method <- do.call(
				rbind,
				lapply(names(rev_by_method), function(method){
					rev_meth <- rev_to_table(rev_by_method[[method]])
					cbind(Meth = method, rev_meth)
				})
			)
			rev_tot_by_method <- rev_tot_by_method[rev_tot_by_method[, "Last date"] != colnames(rev_tot_by_method)[4], -4]
			rev_tot_by_method
		})
	}

@@

	cat("# ", spec_series[[serie]]$description, "\n")
	if (spec$plots$bymethods$enabled){
		cat("## ", spec$plots$bymethods$name)
		cat("\n\n::::: {.panel-tabset}\n")
		for (methods in names(last_est_s)) {
			cat(sprintf("\n### %s\n\n", gsub("\n", " ", methods)))
			first_date <- time(last_est_s[[methods]]$tc)[length(last_est_s[[methods]]$tc)] - spec$plots$nyears
			range_y <- range(window(ts.union(last_est_s[[methods]]$tc, last_est_s[[methods]]$x), start = first_date))
			cat(knitr::knit_child(text = c(
				"```{r}",
				sprintf("#| label: bymethods-%s-%s", serie, studied_methods[methods]),
				'wrap_plots(all_plots[[methods]]) +
			plot_layout(axes = "collect") &
			theme_bw() & theme(legend.title = element_blank(), legend.position = "bottom") &
			# guides(color=guide_legend(nrow=nrow_legend)) &
			labs(x = NULL, y = NULL) &
			coord_cartesian(xlim = c(first_date, NA), y = range_y)',
			"```",
			""
			), envir = environment(), quiet = TRUE
			))
		}
		cat("\n:::::\n\n")
	}

@@

		cat("## ", spec$plots$byplots$name)
		cat("\n\n::::: {.panel-tabset}\n")
		for (plot in names(byplots)) {
			cat(sprintf("\n### %s\n\n", plot))
			first_date <- time(last_est_s[[1]]$tc)[length(last_est_s[[1]]$tc)] - spec$plots$nyears
			range_y <- range(window(ts.union(last_est_s[[1]]$tc, last_est_s[[1]]$x), start = first_date))
			cat(knitr::knit_child(text = c(
				"```{r}",
				sprintf("#| label: byplots-%s-%s", serie, studied_methods[methods]),
				'wrap_plots(byplots[[plot]]) +
			plot_layout(guides = "collect", axes = "collect") &
			theme_bw() & theme(legend.title = element_blank(), legend.position = "bottom") &
			labs(x = NULL, y = NULL) &
			coord_cartesian(xlim = c(first_date, NA), y = range_y) ',
			"```",
			""
			), envir = environment(), quiet = TRUE
			))
		}

@@

		cat("\n\n::::: {.panel-tabset}\n")
		for (methods in names(rev_data_s)) {
			cat(sprintf("\n### %s\n\n", gsub("\n", " ", methods)))
			first_date <- time(rev_data_s[[methods]])[length(time(rev_data_s[[methods]]))] - spec$plots$nyears
			range_y <- range(window(rev_data_s[[methods]], start = first_date), na.rm = TRUE)
			cat(knitr::knit_child(text = c(
				"```{r}",
				sprintf("#| label: revisions-%s-%s", serie, studied_methods[methods]),
				'autoplot(round(rev_data_s[[methods]], digits)) +
			theme_bw() + theme(legend.title = element_blank(), legend.position = "bottom") +
			labs(x = NULL, y = NULL) +
			coord_cartesian(xlim = c(first_date, NA), y = range_y)',
			"```",
			""
			), envir = environment(), quiet = TRUE
			))
		}

>>>>

		rev_tot <- lapply(series, function(serie) {
			rev_by_method <- lapply(names(studied_methods), function(method){
				data <- rev_data_fixed[[serie]][[method]]
				data_tot <- rev_data[[serie]][[method]]
				rev_tc <- (data[,1] - data)
				rev_tot <- (data_tot[,1] - data_tot)
				rev_tot <- rev_tot
				rev_sa <- rev_tot - rev_tc
				colnames(rev_tc) <- colnames(rev_sa) <- colnames(rev_tot) <- colnames(data_tot)
				list(
					Total = rev_tot, 
					`Due to revisions on SA` = rev_sa, 
					`Due to update of TC model` = rev_tc
				)
			})
			names(rev_by_method) <- names(studied_methods)
			rev_tot_by_method <- do.call(
				rbind,
				lapply(names(rev_by_method), function(method){
					rev_meth <- rev_to_table(rev_by_method[[method]])
					cbind(Meth = method, rev_meth)
				})
			)
			rev_tot_by_method <- rev_tot_by_method[rev_tot_by_method[, "Last date"] != colnames(rev_tot_by_method)[4], -4]
			rev_tot_by_method[with(rev_tot_by_method, order(Meth,`Last date`, Methods)), ]
		})
	}

@@

	cat("# ", spec_series[[serie]]$description, "\n")
	if (spec$plots$bymethods$enabled){
		cat("## ", spec$plots$bymethods$name)
		cat("\n\n::::: {.panel-tabset}\n")
		for (i in seq_along(last_est_s)) {
		    methods <- names(last_est_s)[i]
			cat(sprintf("\n### %s\n\n", gsub("\n", " ", methods)))
			first_date <- time(last_est_s[[methods]]$tc)[length(last_est_s[[methods]]$tc)] - spec$plots$nyears
			range_y <- range(window(ts.union(last_est_s[[methods]]$tc, last_est_s[[methods]]$x), start = first_date))
			cat(knitr::knit_child(text = c(
				"```{r}",
				sprintf("#| label: bymethods-%s-%s", serie, studied_methods[i]),
				'wrap_plots(all_plots[[methods]]) +
			plot_layout(axes = "collect") &
			theme_bw() & theme(legend.title = element_blank(), legend.position = "bottom") &
			# guides(color=guide_legend(nrow=nrow_legend)) &
			labs(x = NULL, y = NULL) &
			coord_cartesian(xlim = c(first_date, NA), y = range_y)',
			"```",
			""
			), envir = environment(), quiet = TRUE
			))
		}
		cat("\n:::::\n\n")
	}

@@

		cat("## ", spec$plots$byplots$name)
		cat("\n\n::::: {.panel-tabset}\n")
		for (plot in names(byplots)) {
			cat(sprintf("\n### %s\n\n", plot))
			first_date <- time(last_est_s[[1]]$tc)[length(last_est_s[[1]]$tc)] - spec$plots$nyears
			range_y <- range(window(ts.union(last_est_s[[1]]$tc, last_est_s[[1]]$x), start = first_date))
			cat(knitr::knit_child(text = c(
				"```{r}",
				sprintf("#| label: byplots-%s-%s", serie, plot),
				'wrap_plots(byplots[[plot]]) +
			plot_layout(guides = "collect", axes = "collect") &
			theme_bw() & theme(legend.title = element_blank(), legend.position = "bottom") &
			labs(x = NULL, y = NULL) &
			coord_cartesian(xlim = c(first_date, NA), y = range_y) ',
			"```",
			""
			), envir = environment(), quiet = TRUE
			))
		}

@@

		cat("\n\n::::: {.panel-tabset}\n")
		for (i in seq_along(rev_data_s)) {
		    methods <- names(rev_data_s)[i]
			cat(sprintf("\n### %s\n\n", gsub("\n", " ", methods)))
			first_date <- time(rev_data_s[[methods]])[length(time(rev_data_s[[methods]]))] - spec$plots$nyears
			range_y <- range(window(rev_data_s[[methods]], start = first_date), na.rm = TRUE)
			cat(knitr::knit_child(text = c(
				"```{r}",
				"#| fig-height: 5",
				sprintf("#| label: revisions-%s-%s", serie, c("rav", studied_methods)[i]),
				'autoplot(round(rev_data_s[[methods]], digits)) +
			theme_bw() + theme(legend.title = element_blank(), legend.position = "bottom") +
			labs(x = NULL, y = NULL) +
			coord_cartesian(xlim = c(first_date, NA), y = range_y)',
			"```",
			""
			), envir = environment(), quiet = TRUE
			))
		}
